Verifying Demonstrations

### 2017-11-16 contents-poster.tex
Fixes typo, minor edits

    \begin{orangeblock}{Currently most popular method}
      \centering
      \includegraphics[width=0.9\linewidth]{fig/Jacobs-method.jpg}
      \begin{itemize}
        \item Mostly used method, Jacob's method.
        \item Divide the area into regions, estimate the density in each 
          region, sum them up.
        \item \color{red} Cannot handle cumulative counts.
      \end{itemize}
    \end{orangeblock}

@@

    \begin{redblock}{Verifying protest participation}
      \begin{itemize}
        \item {\color{olive!10!green!90} Alice wants to show that many support 
            her cause.}
        \item {\color{red} Eve wants to show that few support Alice's cause.}
        \item Adversarial setting, requires verifiable results!
      \end{itemize}
    \end{redblock}

>>>>

    \begin{orangeblock}{Currently most popular method}
      \centering
      \includegraphics[width=0.9\linewidth]{fig/Jacobs-method.jpg}
      \begin{itemize}
        \item Most used method, Jacob's method.
        \item Divide the area into regions, estimate the density in each 
          region, sum them up.
        \item \color{red} Cannot handle cumulative counts.
      \end{itemize}
    \end{orangeblock}

@@

    \begin{redblock}{Verifying protest participation}
      \begin{itemize}
        \item Alice wants to show that many support her cause.
        \item Eve wants to show that few support Alice's cause.
        \item \color{red} Adversarial setting, requires verifiable results!
      \end{itemize}
    \end{redblock}
